Deriving Multi-Headed Planar Dependency Parses from Link Grammar Parses

### 2014-12-09 doc/slides/hong+eisner.TLT13.slides.tex
improved animations

%\setbeamerfont{page number in head/foot}{}
%\setbeamertemplate{footline}[frame number]

\begin{document}
\title{Deriving Multi-Headed Planar Dependency Parses from Link Grammar Parses}
\author{Juneki Hong, Jason Eisner}
\date{\today}
\frame{\titlepage \NoteJH{Include pictures of us?}}

@@

\frame{\frametitle{Consistency of Directionalized Links}
\begin{itemize}
  \item[] Consistency of Directionalized Links
    \begin{itemize}
      \item[] $r_L, \ell_L \in \{0,1\}$: whether links with label $L$ allowed left/right
    \end{itemize}
    \begin{align}\label{direction+slack}
      x_{ij} &\leq r_L &
      x_{ji} &\leq \ell_L 
    \end{align}
    \begin{align}\label{eqn:obj}
      \min \left( \sum_L r_L + \ell_L \right)
    \end{align}
    \begin{itemize}
      \item[]  
      \item[]  
    \end{itemize}

    \begin{itemize}
      \item[]
    \end{itemize}

\frame{\frametitle{Consistency of Directionalized Links with Slack}
\begin{itemize}
  \item[] Consistency of Directionalized Links
    \begin{itemize}
      \item[] $r_L, \ell_L \in \{0,1\}$: whether links with label $L$ allowed left/right
    \end{itemize}
    \begin{align}\label{direction+slack}
      x_{ij} &\leq r_L + s_{ij} &
      x_{ji} &\leq \ell_L + s_{ij} 
    \end{align}
    \begin{align}\label{eqn:obj}
      \min \left( \sum_L r_L + \ell_L \right) \cdot \frac{N_L}{4} + \sum_{ij}s_{ij}
    \end{align}
    \begin{itemize}
      \item[] $s_{ij} \in \mathbb{R} \geq 0$: slack variable 
      \item[] $N_L$: Number of link tokens with label $L$
    \end{itemize}

    \begin{itemize}
      \item[] Slack allows a few links with label $L$ in disallowed directions
    \end{itemize}

>>>>

\setbeamerfont{page number in head/foot}{}
\setbeamertemplate{footline}[frame number]

\begin{document}
\title{Deriving Multi-Headed Planar Dependency Parses from Link Grammar Parses}
\author{Juneki Hong, Jason Eisner}
\date{\today}
\frame{\titlepage} %\NoteJH{Include pictures of us?}

@@

\frame{\frametitle{Consistency of Directionalized Links \onslide<2->{with Slack}}
\begin{itemize}
  \item[] Consistency of Directionalized Links
    \begin{itemize}
      \item[] $r_L, \ell_L \in \{0,1\}$: whether links with label $L$ allowed left/right
    \end{itemize}

    \begin{align}\label{direction+slack}
      x_{ij} &\leq r_L \onslide<2->{ + s_{ij}} &
      x_{ji} &\leq \ell_L \onslide<2->{ + s_{ij}}
    \end{align}

    \begin{align}\label{eqn:obj}
      \min \left( \sum_L r_L + \ell_L \right) \onslide<2->{\cdot \frac{N_L}{4} + \sum_{ij}s_{ij}}
    \end{align}

    \onslide<2->{\begin{itemize}
      \item[] $s_{ij} \in \mathbb{R} \geq 0$: slack variable 
      \item[] $N_L$: Number of link tokens with label $L$
    \end{itemize}

    \begin{itemize}
      \item[] Slack allows a few links with label $L$ in disallowed directions
    \end{itemize}
    }
